_FILETYPE
VERSION	 1.0
DEFAULT	 ON
NAME	"Wet"
_END


_DESCRIPTION


Wet                                      lume
---------------------------------------------


       Wet objects have a significantly
       different appearance than dry ob-
       jects: some have more saturated
       colors, others acquire a specular
       highlight. The Wet shader facili-
       tates the creation of this effect
       by swapping textures for surfaces
       that are `wet'.

       [IMAGE]



  Procedure

        Apply a dry-looking texture to the
        object.

        Apply a wet-looking texture to the
        object. (On top of the dry-looking
        one.)

        In the wet-looking texture's dia-
        logue box, select Alpha-Channel
        Mask as the blending.

        In the wet-looking texture's dia-
        logue box, select Wet as the tex-
        ture shader; this designates this
        texture as wet.



  Parameters

       `Wetness' is specified by either
       the WaterSurface or Stain shaders;
       when an object with a texture des-
       ignated as wet is seen through
       the surface of an object which has
       either Stain or WaterSurface ap-
       plied, the wet object will display
       its wet texture. (In the case of
       WaterSurface, the Stain Under-
       neath effect must be selected.)

       Note that if the camera enters the
       water, the textures must be reas-
       signed, as objects that are under-
       water will no longer be seen
       through the surface of the water -
       since the camera itself is now un-
       derwater as well. In this case, the
       dry-looking texture must now be
       placed on top of the wet-looking
       texture; also, the Wet shader would
       be removed from the wet-looking
       texture and applied to the dry-
       looking one instead, since this is
       the texture that the submerged cam-
       era would be seeing through the
       surface of the water. (See the
       LumeWater tutorial for an example
       of this procedure.)

---------------------------------------------

_END


_DIALOG_TEMPLATE
1,	"Wet", 11,	1,	11,	441, 382, 837, 642
   1,	2,	"Ok",		745, 398, 825, 435, 0
   2,	2,	"Cancel",	655, 398, 735, 435, 0
   3,	0,	"User Comment",	457, 488, 565, 503, 0
   4,	0,	"L U M E",	607, 625, 670, 640, 0
   5,	0,	"(No parameters)",574, 557, 709, 572, 0
   6,	0,	"",		506, 591, 526, 606, 0
   7,	0,	"",		497, 578, 517, 593, 0
   8,	0,	"",		505, 563, 525, 578, 0
   9,	2,	"Save",		547, 398, 627, 435, 0
   10,	2,	"Help",		457, 398, 537, 435, 0
   11,	5,	"",		457, 452, 825, 482, 0, MIN, MAX, 0

_SYMBOLS
_END

_EXCLUSIVE
_END



_DATA
dum 0.0
_END


_SHADER_PREVIEWER
PLANE
  ZPOS -80
  SIZE 20 20
  CHECKER
    SQUARE1 0.8 0 0
    SQUARE2 0.8 0 0
    LINE 0.8 0.8 0.8
    SIZE_SQUARE1 0.125
    SIZE_SQUARE2 0.125
    DIFFUSE 0 0 0
SPHERE
  ZPOS -20
  SIZE 5
WINDOW
  POS 10 10
RENDER
  MIN_SAMPLES -5
  MAX_SAMPLES 0

_END


_SHADER_LINKS
LINK, Wet.so
_END

_SHADER_DECLARE
declare,	Wet

scalar,		dum
_END
